---
title: "KHDSS Infant Morality Platform"
output:
  flexdashboard::flex_dashboard:
    orientation: rows
  theme: cosmo

runtime: shiny
---

<style>                     
.navbar {
  border-color:black;
}
.navbar-brand {
color:black!important;
}
</style> 
  
```{r setup, include=FALSE}
#loading of packages for the application
library(flexdashboard)
library(shiny)
#devtools::install_github('hadley/ggplot2')
library(dplyr)
library(tidyr)
library(lubridate)
library(ggplot2)
library(plotly)
library(reshape)
library(doBy)
library(rsconnect)
library(psych)
library(foreign)
library(data.table)
library(gridBase)
library(grid)
library(plotly)
library(xtable)
library(magrittr)
library(kableExtra)
library(tidyverse)
library(devtools)
library(ggsn)
library(ggmap)## calls map from google.
library(maptools)# needed to read the shapefile into R
library(rgdal)
library(scales)
if (!require(gpclib)) install.packages("gpclib", type="source")
gpclibPermit()


#Increasing the default maximum upload restriction of Shiny to 10GB can add to globali
if(Sys.getenv('SHINY_PORT') == "") options(shiny.maxRequestSize=10000*1024^2)





```


Sidebar {.sidebar data-width=300,icon="fa-thumbs-down"}
================================
### Upload Data
```{r}
rm(list=ls())
fileInput("file1", "Upload a .csv, .txt or Excel File",
          multiple = TRUE,
          accept = c(
            
            "text/csv",
            "text/comma-separated-values,text/plain",
            ".csv"))


# Input: Select separator ----
radioButtons("sep", "Separator",
             choices = c(Comma = ",",
                         Semicolon = ";",
                         Tab = "\t"),
             selected = ",")

# Input: Select quotes ----
radioButtons("quote", "Quote",
             choices = c("None" = "",
                         "Double Quote" = '"',
                         "Single Quote" = "'"),
             
             selected = '"')


sliderInput("no_records", "Select the number of records to view:",
            min = 0, max = 1000,
            value = 500)

## for inteli section
data1 <- read.csv("/Users/damadi/Desktop/samp_data/infantdatafinal15.csv")
data2=readShapePoly("/Users/damadi/Desktop/samp_data/shapefile/DSS_sublocations.shp")
infants <- read.csv("/Users/damadi/Desktop/samp_data/infantdatafinal15.csv")
infants <-as.data.frame(infants)
coverage <-table(infants$immun)
coverage <-as.data.frame(coverage)
data <- coverage[,c('Var1', 'Freq')]


###Guage anc attendance

anc <-as.data.frame(table(infants$anc_attended))



#Group attendance to ANC
anc<-infants %>%
  group_by (anc_attended) %>%
  summarise (n=n()) %>%
  mutate(freq = paste0(round(100 * n/sum(n), 0), "%"))

anc$anc_attended <- factor(anc$anc_attended, levels = c(0,1,6,99),
labels = c("Not Attending", "Attending","Error", "Dont Know"))

#preparing data for ploting bar graph
df <-as.data.frame(infants)
missing.age <- is.na(df$mum_age)
df <- df[!missing.age,]  # select only those not missing ages
labs <- c(paste(seq(0, 95, by = 5), seq(0 + 5 - 1, 100 - 1, by = 5),
                sep = "-"), paste(100, "+", sep = ""))
#labs

df$AgeGroup <- cut(df$mum_age, breaks = c(seq(0, 100, by = 5), Inf), labels = labs, right = FALSE)
#head(df[c("mum_age", "AgeGroup")], 15)

#collapse
df1 <-table(df$AgeGroup)
df1 <-as.data.frame(df1)

agegroups <-as.data.frame(filter(df1, Freq >0))



```

DATASET
============

Row
-------------------------------------

### **View Data**

```{r}
df_k <- reactive({
  if(is.null(input$file1))     return(NULL)
  df_ken <- read.csv(input$file1$datapath,
                 sep = input$sep,
                 quote = input$quote) 
  
 # df_ken <- df_ken[complete.cases(df_ken),]
  })

output$tableK <- DT::renderDataTable({

  # input$file1 will be NULL initially. After the user selects
  # and uploads a file, head of that data file by default,
  # or all rows if selected, will be shown.

  req(input$file1)

  df <- DT::datatable(df_k() , options = list( bPaginate=T, bFilter=T))

  })

 DT::dataTableOutput('tableK')
```

Row
-------------------------------------
   
### **Data Structure**

```{r}
 output$data <- DT::renderDataTable({
  
      dfc <-as.data.frame(df_k())
       variables <-ncol(dfc)
        obs <-nrow(dfc)
        clas <-class(dfc)
      s_list <- data.frame(id=c("The number of variables","The number of observations","Data Class" ), Value=c(variables,obs,clas))
      
        s_list <- DT::datatable(s_list, options = list(bPaginate = FALSE,bFilter=FALSE,bInfo=FALSE,scrollCollapse=TRUE,autowidth=FALSE))

       
        
 })
  
DT::dataTableOutput('data')
```   
    
### **Summary Statistics**

```{r}
output$summary <- renderPrint({
    
      dfc <-as.data.frame(df_k())
      nums<-sapply(dfc,  is.numeric)
      #describe(dfc[,nums],IQR=FALSE)            
      summary(dfc[,nums])
   
  })
  
verbatimTextOutput("summary")


```

Over-View
====

Row
-----------------------------------------------------------------------

### Participants 2015

```{r}
output$articles <- renderValueBox({
  pop <- as.data.frame(infants)
  
valueBox(paste(nrow(pop)), subtitle="Infants", icon = NULL, color = "blue", width = 4,
  href = NULL)

})

valueBoxOutput("articles")


# output$articles <- renderValueBox({
#   pop <- as.data.frame(infants)
# valueBox(
#      paste0(nrow(pop)),
#      icon = "fa-comments",
#     color = "olive")
# })

#valueBoxOutput("articles")


```

### Female: Male ratio


```{r}

# output$malefemale <- renderValueBox({
#   v<-as.data.frame(round((table(infants$sex)/table(infants$sex)[2])*100,0))
#   x<-paste(v$Freq[1], v$Freq[2], sep=":")
# print(x)
# })
# 
# valueBoxOutput("malefemale")

#tags$b

output$malefemale <- renderPrint({
    
  v<-as.data.frame(round((table(infants$sex)/table(infants$sex)[2])*100,0))
  x<-paste("<b>",v$Freq[1], v$Freq[2], sep=":""</b>")
 
 cat(x)
 
 #fruits[input$index] <- paste("<b>",fruits[input$index],"</b>")
   
  })
  
verbatimTextOutput("malefemale")

```


### ANC Coverage

```{r}

  gauge(anc$freq[2], min = 0, max = 100, gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))    



```

### Immunisation Proportion:

```{r}

plot_ly(data, labels = ~Var1, values = ~Freq, type = 'pie',textinfo = 'label+percent') %>%
  layout(title = '',
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))





```

   
Row
-------------------------------------
    
### Kilifi infants Death Rate
    
```{r}

data1_sum <- data1 %>% group_by(sublocn) %>% 
  summarise(n=n(), mean_subloc=mean(status)) %>% 
  mutate(mean_subloc=mean_subloc*100)


##converting the map to a data frame


klf_shp <- ggplot2::fortify(data2, region = "SLNAME")

# str(klf_shp)
# str(data1_sum)

data1_sum$sublocn <- as.factor(data1_sum$sublocn)
data2 <- klf_shp %>% left_join(data1_sum, by=c("id" = "sublocn"))

#str(data2)

#incidence death

p<-ggplot(data2) + 
  aes(long, lat, group = group, fill = mean_subloc) + 
  geom_polygon() + 
  geom_path(color="black") +
  coord_equal() +
  scale_fill_gradient2(low = "indianred1",mid = "indianred4",midpoint = 4, high = muted("darkred"),
  limits = c(0, 8)) +
  theme_bw() + xlab("Longitude") + ylab("Latitude") +
  theme(axis.text=element_text(size=13),legend.title=element_text(size=13),
                 axis.title=element_text(size=22,  face="bold")) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
               panel.background = element_blank(), axis.line = element_line(colour = "black"),
               panel.border = element_rect(colour="white"))


print(p)

```
    
### Infants Mothers Age Groups

```{r}



names(agegroups)[1]<-"AgeGroup"

plot_ly(agegroups, x = ~AgeGroup, y = ~Freq, type = 'bar', name = 'SF Zoo') %>%
  layout(yaxis = list(title = 'Count'), barmode = 'group')



```



GRAPHS
====
Row {data-height=300}
-------------------------------------

### variable:

```{r}
output$variable <- renderUI({

    stat <- data.frame(df_k())
    inputPanel(
    selectInput("variable","",names(stat))
      #selectInput("variable","",names(stat),multiple=TRUE)

    )
})

uiOutput('variable')

```



### Groups:

```{r}

output$group <- renderUI({

    sta <- data.frame(df_k())
    inputPanel(
    selectInput("group","",names(sta))
    

    )
})

uiOutput('group')



```



Row {data-height=700}
------------------------------------

### Plot

```{r}


output$mortalityPlot <- renderPlotly({
  dfp <-as.data.frame(df_k())
 
	#nums<-sapply(dfc,  is.numeric)
  #if(input$plot.type=="boxplot"){
  if(is.numeric(dfp[,input$variable])){
    bplot <- ggplot(data=dfp, aes_string(y=input$variable, x=input$group,
                                         fill=input$group)) +
      geom_boxplot()+ theme_minimal()
      #geom_boxplot() + geom_jitter(alpha=0.6)+ theme_minimal() **includes scatter plot but noisy
ggplotly(bplot)
    #boxplot(dfp[,input$variable]~dfp[,input$group])
  #}else if(input$plot.type=="bar"){
  }else if(is.character(dfp[,input$variable])){
   if(is.numeric(dfp[,input$variable])){
     id <<- showNotification(paste("Use Categorical Variable"), duration = 10,type ="error")
   }else(removeNotification(id))
  bplot <- ggplot(data=dfp, aes_string( x=input$group,
                                         fill=input$variable)) + 
    geom_bar(position="dodge") + theme_classic()
  
  ggplotly(bplot)
    
  }else {
    print("error")
  }
  
  
  
  
  
 
  })

 plotlyOutput("mortalityPlot")



```



EXPLORATORY ANALYSIS
============

Row
-------------------------------------
    
### Tabulation
    
```{r}

output$tabulation <- renderUI({
 
   xx <- data.frame(df_k())
              inputPanel(
            selectInput("vits", "Column variable",names(xx))


          )
})

 uiOutput("tabulation")
 

```

### Tab Results


```{r}
output$tableT <- renderTable({

      dft <- as.data.frame(df_k())
      #v<-data.frame(tableStack(dft[, input$row], by=dft[, input$column], data=df, test=FALSE))
     # v<-v[v$Var1!="", ]
      #reshape(v, idvar="Var1",timevar="Var2",direction="wide")
  
  # Tabulation   
xx<-data.frame(table(dft[, input$vits]))
  
  
  xx<-within(xx, {
  prop<-round(100*(xx$Freq/sum(xx$Freq)),2)
  counts<-paste(Freq, " (", prop, ")", sep="")
})
  
  vw<-xx[, c("Var1","counts")]

  # Totals 
  totals1<-data.frame(Var1="Totals", counts=sum(xx$Freq))

  # Append the datasets
  vw<-rbind(vw,totals1)

  # Rename Var 1
 # names(vw)[1]<-"Education"
 
  names(vw)[1]<-input$vits
  vw

})

tableOutput('tableT')     
      

```

   
Row
-------------------------------------
    
### Cross Tabulation
    
```{r}

#reactive({
output$kichwa <- renderUI({


              xx <- data.frame(df_k())
              inputPanel(
            selectInput("column", "Column variable",names(xx), selected = "gender"),
            selectInput("row", "Row variable", names(xx), selected = "beer")

          )
})

uiOutput('kichwa')

```
  

### Results 
```{r}

output$tableM <- renderTable({
      dft <- as.data.frame(df_k())
      #v<-data.frame(tableStack(dft[, input$row], by=dft[, input$column], data=df, test=FALSE))
     # v<-v[v$Var1!="", ]
      #reshape(v, idvar="Var1",timevar="Var2",direction="wide")
  
  # Tabulation   
  v<-data.frame(table(dft[, input$row], dft[, input$column]))
  
  
  x<-v %>%
    group_by(Var1) %>%
    summarise(totals = sum(Freq))

  w<-merge(v,x, by.x="Var1", by.y="Var1")
  w<-within(w, {
   prop<-round((Freq/totals)*100, 2)
    counts<-paste(Freq, " (", prop, ")", sep="")
  })

# Totals
    t<-w[!duplicated(w$Var1), ]
    t<-t[, c("Var1","Var2","totals")]
    names(t)[3]<-"counts"
    t<-reshape(t, direction="wide", idvar="Var2", timevar="Var1")
    t$Var2<-as.character(t$Var2)
    t[1,1]<-"Total"


w<-w[, c("Var1","Var2","counts")]
w<-reshape(w, direction="wide", idvar="Var2", timevar="Var1")
w<-rbind(w,t)
names(w)[1]<-input$column
w<-w %>%
  set_names(~ str_to_lower(.) %>%
              str_replace_all("counts.", ""))

w
})

tableOutput('tableM')
```




REGRESSSION
====
Row {data-height=300}
-------------------------------------

### Select ONE variable as dependent variable:

```{r}

output$dependent <- renderUI({
    df <- data.frame(df_k())
    if (is.null(df)) return(NULL)
    items=names(df)
    names(items)=items
    selectInput("dependent","",items,selectize=TRUE)

  })

 uiOutput("dependent")

```


### Select ONE or MORE independent variables:

```{r}

output$independents <- renderUI({
  df <- data.frame(df_k())
  if (is.null(df)) return(NULL)
  items=names(df)
  names(items)=items
  selectInput("independents","",items,multiple=TRUE)
})

uiOutput("independents")

```

### Run Logistic regression

```{r}

output$action <- renderUI({
     inputPanel(
    actionButton("action", "Run Logistic regression")
   )
 })

 uiOutput("action")

```

Row {data-height=700}
-------------------------------------

### Here's the output from your regression

```{r}

output$contents <- function() {
    if (is.null(input$action)) return()
    if (input$action==0) return()
    isolate({
      df <- df_k()
      if (is.null(df)) return(NULL)
      fmla <- as.formula(paste(input$dependent," ~ ",paste(input$independents,collapse="+")))
      #summary(glm(fmla,data=df,family=binomial()))

      # a. Logistic regression
  logistic_fun <- function(data, formula = fmla) {
     lm1 <- glm(formula = formula, data = df,family=binomial())

    coefs = round(exp(coef(summary(lm1))[,1]),3)[-1]  # Coefficients
    cis = round(exp(confint(lm1)),2)[-1,] # CI's
    p_value=round(coef(summary(lm1))[,4],3)[-1] # P-values
    output<-data.frame(cbind(coefs, cis, p_value))
    names(output)[2:3]<-c("low", "high")
    output$ci<-paste(output$low, output$high, sep = ", ")
    output$Variable<-rownames(output)
    rownames(output)<-NULL
    output<-output[, c("Variable","coefs", "ci", "p_value")]
    # output <- DT::datatable(output, options = list(bPaginate = #FALSE,bFilter=FALSE,bInfo=FALSE,scrollCollapse=TRUE,autowidth=FALSE))
    # output
    output <-output %>% kable('html') %>% kable_styling("striped",full_width=TRUE) %>%
      row_spec(which(output$p_value<0.1), color="white", background="#CCC") %>%
    footnote(general = "Here is a general comments of the table. ",
           number = c("The highlighted column has a significant relationship"),
           # alphabet = c("Footnote A; ", "Footnote B; "),
           # symbol = c("Footnote Symbol 1; ", "Footnote Symbol 2")
           )



    output
  }
  logistic_fun(df)



    })
  }

#verbatimTextOutput('contents')
#DT::dataTableOutput('contents')
tableOutput('contents')

```



TRENDS
====

Row {data-height=300}
-------------------------------------
  
### Select outcome variable:
  
```{r}
output$status <- renderUI({
  df <- data.frame(df_k())
  if (is.null(df)) return(NULL)
  items=names(df)
  names(items)=items
  selectInput("status","",items,selectize=TRUE)

})

uiOutput("status")

```

### Select date for calculation:

```{r}

output$dates <- renderUI({
  df <- data.frame(df_k())
  if (is.null(df)) return(NULL)
  items=names(df)
  names(items)=items
  selectInput("dates","",items,selectize=TRUE)
  
})

uiOutput("dates")

```

### Display Graph

```{r}
output$display <- renderUI({
    inputPanel(
      actionButton("display", "Display infant mortality Rate")
    )
  })

uiOutput("display")


```

Row {data-height=700}
-------------------------------------
  
### Here's the Infant Mortality Trends
  
```{r}

output$trend <- renderPlotly({
  if (is.null(input$display)) return()
    if (input$display==0) return()
  dat <-as.data.frame(df_k())


# Convert into date
dat$date  <-as.Date(dat[,input$dates], "%m/%d/%Y")

# Create month and year
#dat$month<-month(dat$date)

dat<-within(dat, {
    month<-month(date) #month
    year<-year(date) #year
}
)

# Change Status for January 2015 to blanks ??  comment below line if years are many
dat$status[dat$status==1 & dat$year==2015 & dat$month=="Jan"]<-0

# Number died by month and year
number_died<-dat %>%
    group_by(year,month) %>%
    summarize(number_died = sum(!!as.name(input$status)))

# Number of live births by year and month
number_live_births<-dat %>%
  group_by(year,month) %>%
  summarize(number_live_births =n())

# Merge summary datasets
monthly_counts<-merge(x=number_died,y=number_live_births, id.x=c(year,month), id.y=c(year,month), all=T)

# # Number died and live births by month and year
# monthly_counts<-dat %>%
#   group_by(year,month) %>%
#   summarize(number_died = sum(status),number_live_births =n())

# Proportion died by month and year
monthly_counts<-within(monthly_counts,{
  prop<-(number_died/number_live_births)*1000
  study_month<-1:nrow(monthly_counts) # Counter for months from the start of the study
})

# Labels for year
yearlab<-unique(monthly_counts$year)
yearlab<-yearlab[1:2] # comment if data has all the months

# Plot monthly counts
p<-ggplot(monthly_counts, aes(x=study_month, y=prop)) + geom_point() +
  geom_line() +
  theme(axis.text.y=element_text(colour="black", hjust=1),
        axis.text.x=element_text(colour="black", hjust=-5, vjust=1)) +
  xlab("Months") + ylab("Death rate per 1,000 live births") +
  coord_cartesian(xlim=c(1:nrow(monthly_counts))) +
  scale_x_continuous(breaks=seq(1,nrow(monthly_counts),11) , labels=yearlab) +
  theme(panel.grid.major=element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  ggtitle("Monthly death") + theme(plot.title = element_text(hjust = 0.5, face="bold"))

ggplotly(p)


  })


 plotlyOutput("trend")
     


```

Spatial Distribution
====

### **Display For Spartial Distribution of Infant Mortality:**

```{r}

  shinyAppDir(
 
  "/Users/damadi/Documents/WITS/Project/ResearchReport/app/other/SpatialAppKhdss" )

```



